RJObject Paper

### 2014-06-09 Documents/Paper/ms.tex
hierarchical again

We would like to assign a prior to the objects' properties $\{x_i\}_{i=1}^N$.
Since $N$ may be large, it is usually easier to assign an ``interim prior''
conditional on some hyperparameters $\alpha$.

>>>>

We would like to assign a prior to the objects' properties $\{x_i\}_{i=1}^N$.
Since $N$ may be large, it is usually easier to assign an ``interim prior''
conditional on some hyperparameters $\alpha$, and then assign a prior to
$\alpha$. This kind of model is usually called {\it hierarchical}.
